\chapter{Conclusions, Limitations, and Future Work} \label{Sec: Concluding Chapter}

In this chapter, we place the results of \Cref{Sec: Paper Chapter} into context with the overall theory of galaxy evolution and co-evolution in \cref{Sec: Conclusion Conclusions}. The limitations of the thesis are briefly discussed in \cref{Sec: Limitations}, and finally, the directions of future work are explored in \cref{Sec: Future Directions}.

\section{Conclusions} \label{Sec: Conclusion Conclusions}

We utilised ZFOURGE data as inputs for CIGALE to separate the SF and AGN components of the infrared spectral energy distribution to create and analyse their respective luminosity functions. Our results are summarised as follows:

\begin{enumerate}[(i)]
    \item We first generate LFs of ZFOURGE galaxies from a sub-sample of 18,373 galaxies that accounted for incompleteness and bias across various redshift bins ranging from $0<z<6$.
    
    \item After CIGALE decomposition, we find 21,390 sources (28.9\% of the sample) with a significant AGN fraction ($\mathcal{F}_{AGN} > 0.1$). This was reduced to 16,850 sources (22.8\%) after an 80\% flux completion cut. In context with AGN dominant sources removed in ZFOURGE by \cite{cowley_zfourge_2016}, simple MIR colour-colour selection diagnostics are insufficient to identify low luminosity AGN, which we show significantly influences galaxy samples.
    
    \item We use a Saunders function to fit CIGALE SF LFs, although a Schechter function may fit too, as predicted by \cite{wu_mid-infrared_2011, fu_decomposing_2010}. Brighter SF galaxies at higher redshifts are required to confirm. 

    \item A peak and turnover in the evolution of CIGALE SF $L^{*}$ is found at $z \approx 2$ coinciding with the peak of cosmic star formation. Similarly, SF LD is also seen to peak and decline above $z\approx2$. This agrees with established literature and provides good evidence supporting our CIGALE results. Importantly, no turnover in ZFOURGE LD was found, highlighting the importance of SED decomposition.
    
    \item A peak and turn over in $\phi^{*}$ is seen for CIGALE AGN at $z \approx 2$ with $L^{*}$ continuing to decline. Although the AGN LD declines from $z<2$, above $z>2$ does not show a defined peak. The peak of AGN LF likely lies between $z\approx2.5-3.5$. \cite{delvecchio_tracing_2014} finds a similar trend at the same time for their AGN $\phi^{*}$, but declines below $z<1$. \cite{katsianis_evolution_2017} also shows AGN feedback significantly affects SF at $z<1$. We have found reliable evidence that $z\approx2$ is a significant evolutionary epoch for AGN evolution where the brightest AGN decline. 
    
    \item In context, $L^{*}_{SF}$ peaks at the same time as $\phi^{*}_{AGN}$ while $\phi^{*}_{SF}$ increases across all cosmic time. These results show fainter SF galaxies becoming increasingly common in the local universe while brighter SF galaxies trend towards extinction.  

    \item The space density evolution of luminosity classes for SF and AGN are very different. SF LIRGs and ULIRGs increase in number density and peak at $z \approx 2$ before rapidly declining to the present day. SF FIRGs evolve similarly across fainter luminosities and peak at a lower redshift. The faintest SF FIRGs have yet to peak in number density. AGN number densities peak much earlier in the universe than SF counterparts. Luminous and ultraluminous AGN have declined since at least $z \approx 3$ and likely even earlier. There is a strong correlation between peak AGN density and luminosity. Fainter AGN peak much later in the universe and have declined since $z \approx 2$. This shows a clear \textit{downsizing} effect which is more prominent in AGN.

    \item From high redshift until $z\approx2$, stars formed with increasing brightness and consume a significant fraction of the available gas supply. Below $z<2$, the faintest stars grow in number, but not as big and bright at $z<2$ as the gas supply becomes increasingly exhausted. This is reflected in our class evolution results and is the likely reason behind the \textit{downsizing} effect.

    \item The brightest AGN are already in decline at the beginning of the universe. These AGN decline at a consistent rate until $z\approx2$. Conversely, the faintest AGN increase in number density until $z\approx2$. Below $z=2$, all AGN show a rapid decline. At $z\approx1$, the brightest AGN show signs of increasing in number. This increase appears to last until $z\approx0.5$ before declining again. This reflects a period where the available gas supply shifted to fueling AGN growth.
\end{enumerate}

We expand upon previous literature (e.g. \citealp{rodighiero_mid-_2010, gruppioni_herschel_2013, magnelli_deepest_2013}) significantly. Our results are novel in that we directly compare AGN to SF across various brightness levels simultaneously. We have directly compared the co-evolution of SF with AGN activity. Our results extend fainter and probe higher redshift that previous surveys. These results indicate a scenario where the available gas supply favoured SF from high redshift until $z\approx2$ when the supply becomes increasingly exhausted. Below $z<2$, the remaining gas predominantly had fainter SF, with bright SF rapidly declining to near extinction by $z\approx1$ when number densities stabilise. By $z=1$, the brightest AGN are almost as equally common as the brightest SF. Given that AGN of a particular brightness decline sooner than equally bright SF counterparts, it is probable that AGN positively influences the growth of SF.