\chapter{Acknowledgements}
\thispagestyle{empty}

I want to thank all the people who helped me achieve my dream of studying Astrophysics.
\vspace{1em}

\noindent Firstly, to my Principal Supervisor, Dr Michael Cowley. You're a fantastic teacher and leader who always pushed me to be my best. I wish you could be my supervisor forever. I hope my future supervisors are as kind and thoughtful as you are. I also thank my Associate Supervisor, Professor Nunzio Motta, for his help. 
\vspace{1em}

\noindent To my fellow MPhil students and the QUT Astrophysics Group --- thank you for keeping me sane throughout this journey. Even though productivity often correlated with fewer of us in the office, we created unforgettable memories. I appreciate you all for indulging my terrible jokes and for all the laughter.
\vspace{1em}

\noindent To the School of Chemistry and Physics, the Faculty of Science, the Graduate Research Centre, and the College of Excellence for providing me with support. I am particularly thankful to Jennifer Grossi, Jennifer MacLeod, Wendy Laver, Jill Blacker, and Marvin Fox.

\noindent This research was supported by an Australian Government Research Training Program Scholarship and I acknowledge the Australian Commonwealth Government’s contribution in relation to the RTP scholarship.
\vspace{0.5em}

\noindent To my twin brother, whom I couldn't have done this without.
\vspace{0.5em}

\noindent To the rest of my family, who never stopped believing in me.
\vspace{0.5em}

\noindent To my lovely partner, the real star in my eyes. 
\vspace{0.5em}

\noindent To my friends, no, I'm not done studying yet.
\vspace{0.5em}

\noindent To myself, for never giving up.
\vspace{0.5em}

\begin{center}
    \textit{And finally, to the universe, I'm coming for you...}
\end{center}